Tables/Graphs for Article

### 2017-12-15 article submission/draft1.tex
edited methods, fixed rounding on pvalues, edited appendix

Questions analyzed were restricted to those posted in English. Time until event was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times in the data (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6208 questions, and each test set contained 1552 questions. Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model. Distributions of continuous variables were assessed. Each categorical and continuous predictor, both with and without square root and log transformations, were entered into separate univariate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model. For continuous predictors, the lowest p-value was used to determine if and which transformation was necessary. To determine whether or not splines on continuous predictors were necessary, as well as the optimum number of knots, univariate analysis was again performed. Continuous variables (with transformations found to be necessary in the previous univariate analysis) were again fit to separate univariate Cox models with: no splines and restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{}Harrell2015. All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.

In each fold of cross-validation, the full model was built on one training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}. Signficant results would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}. Metrics were computed for each training and test set. Averages of metrics across test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Martingale residuals were evaluated to assess functional form of each continuous predictor. Deviance residuals were used to identify outliers, or questions poorly predicted by the model. Score residuals were used to identify questions that highly effected parameter estimates. Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time. Significant correlations indicate that a predictor has violated this assumption.

@@

  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data). Of those questions, 4951 (63.8}\%) received an answer by the download date. The shortest answer time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

@@

% Univariate analysis on quantitative predictors
\begin{table}[ht]
\centering
\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ 
  \hline
  *Square root transformation of the number of characters in a question's text & 0.00 \\ 
  \hline
  Number of characters in a question's text (untransformed) & 0.00 \\
  \hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.00 \\ 
  \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
  \hline
  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
  \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
  \hline
  *Square root transformation of the number of characters in the user-defined device title & 0.00 \\ 
  \hline
  *Square root transformation of the average number of characters in a question's tags & 0.00 \\ 
  \hline
  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
  \hline
  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
   \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
  \hline
  Day of the week the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's text is in all lower case & 0.00 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.00 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all * of quantitative predictors were entered into the full model. Restricted cubic splines were fit to all * quantitative variables.

% Splines
\begin{table}[ht]
\centering
\caption{Determining the optimal k number of splines for each predictor} 
\begin{tabular}{| p{5cm} | l | l | l |}
  \hline
  Predictor & K & p-value & AIC \\ 
  \hline
  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
  & 0 & 0.00 & 65862.83 \\ 
  & 5* & 0.00 & 65862.02 \\ 
  & 4 & 0.00 & 65863.35 \\ 
  & 3 & 0.00 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
  & 0 & 0.00 & 65890.28 \\ 
  & 5 & 0.00 & 65884.70 \\ 
  & 4 & 0.00 & 65882.98 \\ 
  & 3* & 0.00 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
  & 0* & 0.00 & 65890.75 \\ 
  & 5 & 0.00 & 65891.69 \\ 
  & 4 & 0.00 & 65891.75 \\ 
  & 3 & 0.00 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
  & 0 & 0.00 & 65922.76 \\ 
  & 5* & 0.00 & 65853.56 \\ 
  & 4 & 0.00 & 65882.07 \\ 
  & 3 & 0.00 & 65881.39 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
  & 0 & 0.00 & 65923.26 \\ 
  & 5 & 0.00 & 65912.11 \\ 
  & 4* & 0.00 & 65910.10 \\ 
  & 3 & 0.00 & 65912.38 \\ 
   \hline
\end{tabular}
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.

% Cross-validation metrics
\begin{table}[ht]
\centering
\caption{Average performance metrics for training and test sets} 
\begin{tabular}{rrrrrrrr}
  \hline
 & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
  \hline
  Training Set & 2.00 & 959.49 & 0.00 & 0.14 & 64729.80 & 0.27 & 0.64 \\ 
  Test Set & 1.96 & 225.44 & 0.00 & 0.14 & 13453.18 & 0.26 & 0.63 \\ 
   \hline
\end{tabular}
\label{table:cv}
\end{table}

% Final metrics for full data 
\begin{table}[ht]
\centering
\caption{Performance metrics for model fit to the full data} 
\begin{tabular}{rrrrrrrr}
  \hline
  HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
  \hline
  2.00 & 1192.32 & 0.00 & 0.14 & 83128.28 & 0.27 & 0.63 \\ 
   \hline
\end{tabular}
\label{table:finalmetrics}
\end{table}

@@

This study developed a Cox regression model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant). While overall the model was signficant, its predictive performance was considerably low.

@@

device

The original device categorization variable, as defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. This variable also contained a considerable amount of NAs (1954, or 25.2\% of all questions). NAs are a result of users asking questions for devices not already in the website's database, or from the user incorrectly defining the device.

This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base. Questions that made the device clear were categorized accordingly. However there were a number of questions that did not explicitly declare the device their question pertained too. These questions were categorized as ``Other''. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''. Appliance and Household categories of the original variable were merged into ``Home''. ``Car and Truck'' were added to the ``Vehicle''. Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''. All other categories remained the same as the original category. The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.

contain answered and unanswered

  These variables were created based on the intuition that certain topics might be more popular, and even unpopular, among the answering community, and that questions concerning these topics might recieve an answer faster, or slower, than questions that don't.

  To create these variables, the data was separated between answered and unanswered questions. Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions. For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions. To determine the latter, a ratio of proportions was assessed. This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20). As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1). Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list. The resulting list for answered questions was 111 words, and 32 words in uanswered questions. Contain\_answered and contain\_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.

111 terms found to be ``frequently-used'' among answered questions (ordered from highest frequency): 
screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top

32 terms found to be ``frequently-used'' among unanswered questions (ordered from highest frequency):
sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit

Text\_contain\_punct

A logical variable indicating true if the question’s text contains any end punctuation marks (. ? !). This variable was created to investigate if run-on sentences, or sentences with no end punctuation, take longer to receive an answer.

Prior\_effort

Logical variable indicating true if the asker used words that indicate prior effort or research was done before asking the question (e.g. ``tried'', ``attempted'', ``tested''). This variable was created based off of findings from \cite{Bhat2014}.

Avg\_tag\_score

This variable was created to investigate the idea that some tags are more popular, or widely used than other, and that including such tags might increase the likelihood of that question recieving an answer. This variable is the average frequency, or proportion of times a question's tags appear in all of the data set. If a question has a higher average, than at least one of it's tags are frequently used. This variable was created based off of findings from \cite{Bhat2014}.

Device\_length

The number of characters in the user-defined device variable. This variable was included to capture when a user incorrectly inputs the device name. For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One” and is 136 characters long. 11 questions in this data set also didn’t include any device. This variable was created based on the intuition that users who incorrectly define their devices make it harder for answerers to discern the topic of their question, and thus have longer answer times or might not recieve an answer.

Avg\_tag\_length

The average number of characters in each question's user-defined tags. If a question did not include a tag, this variable was set to 0. This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system. For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters. It is hypothesized that users who use the tagging system correctly, as with the latter user, receive answers quicker than the former user.

Newline\_ratio

This ratio of the number of newlines to the number of characters in the question's text. This variable was based on the intuition that question's that include newlines in the text are easier to read and thus have faster answer times. Questions with long text that also include newlines are generally easier to read than questions that don’t include any.

>>>>

Questions analyzed were restricted to those posted in English. Time until event was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training sets and five test sets. Univariate analysis, performed on one training set, was used to identify variables and transformations to potentially include in the final Cox model. Distributions of all continuous predictors, both with and without square root and log transformations, were assessed. Each categorical and continuous predictor, both untransformed and transformed, were entered into separate univariate Cox models, and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model. For continuous predictors, the p-value was used to determine which form of the predictor to include---transformed or untransformed. To investigate the use of splines on continuous predictors, univariate analysis was again performed. Continuous variables (with transformations previously found to be necessary) were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines. AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}. All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance \citep{Chen}. Signficant results would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Martingale residuals were evaluated to assess functional form of each continuous predictor. Deviance residuals were used to identify outliers, or questions poorly predicted by the model. Score residuals were used to identify questions that highly effected parameter estimates. Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time. Significant correlations would indicate that a predictor has violated this assumption.

%----------------------------------------------------------------------------------------------------

@@

  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data). Of those questions, 4951 (63.8}\%) received an answer by the download date. The shortest answer time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows that the distribution of answer times for all questions is extremely right-skewed.

@@

% Univariate analysis on quantitative predictors
\begin{table}[ht]
\centering
\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ 
  \hline
  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ 
  \hline
  Number of characters in a question's text (untransformed) & 6.9472e-12 \\
  \hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ 
  \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ 
  \hline
  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ 
  \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ 
  \hline
  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ 
  \hline
  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ 
  \hline
  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ 
  \hline
  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ 
   \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ 
  \hline
  Whether or not the question's text is in all lower case & 1.5400e-7 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ 
  \hline
  Day of the week the question was posted & 7.8677e-4 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

Each training set contained 6208 questions, and each test set contained 1552 questions. Results of univariate analyis, performed on one training set, for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors, as well as all continuous predictors marked with * were entered into the full model.

% Splines
\begin{table}[ht]
\centering
\caption{Determining the optimal k number of splines for each predictor} 
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  Predictor & K & AIC \\ 
  \hline
  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
  & 0 & 65862.83 \\ 
  & 5* & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & 3* & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
  & 0* & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
  & 0 & 65922.76 \\ 
  & 5* & 65853.56 \\ 
  & 4 & 65882.07 \\ 
  & 3 & 65881.39 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
  & 0 & 65923.26 \\ 
  & 5 & 65912.11 \\ 
  & 4* & 65910.10 \\ 
  & 3 & 65912.38 \\ 
   \hline
\end{tabular}
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model.

% Cross-validation metrics
\begin{table}[ht]
\centering
\caption{Average performance metrics for training and test sets} 
\begin{tabular}{rrrrrrrr}
  \hline
 & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
  \hline
  Training Sets & 2.0164 & 937.2018 & 0.0000 & 0.1401 & 64752.0898 & 0.2693 & 0.6346 \\ 
  Test Sets & 1.9761 & 220.0417 & 0.0000 & 0.1401 & 13458.5808 & 0.2584 & 0.6292 \\
   \hline
\end{tabular}
\label{table:cv}
\end{table}

% Final metrics for full data 
\begin{table}[ht]
\centering
\caption{Performance metrics for model fit to the full data} 
\begin{tabular}{rrrrrrrr}
  \hline
  HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
  \hline
  2.0010 & 1192.3234 & 0.0000 & 0.1424 & 83128.2780 & 0.2698 & 0.6349 \\ 
   \hline
\end{tabular}
\label{table:finalmetrics}
\end{table}

@@

This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant). While overall the model was signficant, its predictive performance was considerably low.

%----------------------------------------------------------------------------------------------------

@@

Device category

Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Of all questions in the data, 1954 questions (25.2\%) contained missing values for this variable. Missing values were a result of users creating questions for devices not already in the website's database, or from the user incorrectly defining the device name. For questions with missing values, key words were searched for in device titles to recategorize accordingly. Remaining questions with ambiguous or completely missing device titles were categorized as ``Other''. The following modifications were made to the original variable: All Apple products (e.g., iPhones, iMacs, Apple watches) were categorized as ``Apple Product''. Remaining phones in the original ``Phones'' category were categorized as ``Android/Other Phone''. Appliance and Household categories of the original variable were merged into ``Home''. ``Car and Truck'' were added to ``Vehicle''. Any category that contained less than 2\% of all questions were categorized as ``Other''. All other categories remained the same as the original variable. Final categories included: Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.

Whether or not the question's title contains terms considered to be frequently used among unanswered/answered questions

Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively.

These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not. Similarly, certain topics might be unpopular. Thus, questions pertaining to those topics might receive answers slower (cite).

The data was separated between answered and unanswered questions. For the data frame containing answered questions, text mining techniques were used to create a list with every word within questions' titles and the frequency, or number of times they occurred among answered questions. The same was performed for the data frame containing unanswered questions. ``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of answered questions' titles, and appeared in more answered questions than in unanswered questions. To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed. The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered frequently-used among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20). As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of unanswered question's titles and occur in more unanswered questions than answered questions. As there was some overlap between words in each list and the device categories, every word that matched a device name was removed from the lists. The resulting list for answered questions contained 111 words. The list for unanswered questions contained 32 words.

``Frequently-used'' terms among answered questions (ordered by decreasing frequency): 
screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top

``Frequently-used'' terms among unanswered questions (ordered by decreasing frequency):
sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit

Whether or not the question's title ended in a questionmark

A logical variable indicating true if the question's title ends in a questionmark. This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.

Whether or not the question's text contained at least one end punctuation mark

A logical variable indicating true if the question’s text contains any end punctuation marks (``.'', ``?'', ``!''). This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.

Whether or not the user made an effort to solve the problem on their own, prior to asking the question

Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g. ``tried'', ``attempted'', ``tested''). This variable was created based off of findings from \cite{Bhat2014}.

Average frequency ``score'' of a question's tags

This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving a faster answer. This variable is the average frequency, or proportion of times a question's tags appear in all of the data set. If a question has a higher average, than at least one of it's tags are frequently used. This variable was created based off of findings from \cite{Bhat2014}.

Number of characters in the user-defined device title

This variable was included to capture when a user incorrectly defines the device name. For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”, and is 136 characters long. 11 questions in the data also did not include any device title. This variable was created based on the intuition that users who incorrectly define their devices, or do not include any device title, make it difficult for the answering community to discern the question's topic, and thus have longer answer times or remain unanswered.

Average number of characters in a question's tags

This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system. For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters. Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag. It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.

Ratio of the number of line breaks to the number of characters in a question's text

This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
